---
title: "Initial Attempt with own Album Collection"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('tidyverse')
library('dplyr')
library('caret')
```

With the data scraping and aggregation completed, let's look at the raw data collected:
```{r, message = FALSE}
albumCovers <- read_csv('data/album-cover-data.csv')

glimpse(albumCovers)
```
The 11 variables in `albumData` are as follows:
* `artist` is the name of the music artist that released the album
* `year` is the studio release
* `title` is the title of the artist's studio release
* `genre` which is our target classifier.
* `faces` are the number of faces found by Google Vision in the album cover
* The *3 colors with the highest scores* are saved in `albumData` as: `primary_color`, `secondary_color`, and `tertiary_color`. Their scores are also saved in the similarly named: `primary_score`, `secondary_score`, and `tertiary_score` for the potential of building interactive terms in linear and logistical models if need be.

```{r}
colSums(is.na(albumCovers))
clean_dat <- albumCovers %>%
  drop_na()
colSums(is.na(clean_dat))
```

There are only 31 artists with missing album `years` as well as 1 record that didn't have a 3rd color. I've elected to remove these rows of data as I feel year will not be a good predicter in determining genre from the album image, which leaves the last observation with a missing 3rd color as insignificant. 

Let's take a look and see how this collection of artists is distributed across years, and genres.

```{r}
clean_dat %>%
  ggplot() +
  geom_bar(aes(x=genre)) +
  coord_flip()
```

I'm definitely a huge fan of Rock and Electronic music. Not a significant amount of artist releases in the other genres! It also appears that some sound track ablums slipped through the scraping filters as `Sound & Stage`. The model would not get enough observations to anything but `Rock` and `Electronic`...so removing all the other genres would be helpful. 

```{r}
clean_dat <- filter(clean_dat, genre == 'Rock' | genre == 'Electronic')
```

```{r}
clean_dat %>%
  ggplot() +
  geom_bar(aes(x=genre)) +
  coord_flip()
```


```{r}
clean_dat %>%
  ggplot() +
  geom_bar(aes(x=year))
```

I'm definitely a child of the 80's and the number of albums don't pick up until then. For a better distribution, I've elected to filter anything older than 1980.

```{r}
clean_dat <- filter(clean_dat, year >= 1980)
clean_dat <- filter(clean_dat, !str_detect(title, 'Tour|Live')) # Remove more non-studio releases
clean_dat <- filter(clean_dat, !str_detect(title, 'New York')) # Remove other live albums
clean_dat %>%
  ggplot() +
  geom_bar(aes(x=year))
```

```{r}
num_raw_albums <- albumCovers %>% nrow()

num_raw_artists <- albumCovers %>%
  group_by(artist) %>%
  count() %>%
  nrow()

albumCovers %>%
  group_by(artist) %>%
  count() %>%
  ungroup() %>%
  summarize(
    avg_releases = mean(n),
    num_albums = num_raw_albums,
    num_artists = num_raw_artists
)
```


```{r}
num_albums <- clean_dat %>% nrow()

num_artists <- clean_dat %>%
  group_by(artist) %>%
  count() %>%
  nrow()

clean_dat %>%
  group_by(artist) %>%
  count() %>%
  ungroup() %>%
  summarize(
    avg_releases = mean(n),
    num_albums = num_albums,
    num_artists = num_artists
)
```
After **NA's** are removed, there are `661` ablums from `231` artists, with an average of `2.8` releases each. In the original raw data there were `865` albums with just over `250` artists averaging `3.3` albums. Not much of a shift in the number of releases, which further shows that most of my music from 1980 onward is Rock and Pop.

```{r}

```

## Machine Learning

Supervised learning is an excellent canditate for training a machine on album attributes, as we already know the `genre`, we'll train a machine with linear and logistical regressions to see which is most effective in predicting the genre of an album. Interactive terms will also be used to emphasize the color related data variables to tease out more variance.

## Analysis
