---
title: "Pop Quiz"
output: pdf_document
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```



# Please complete the following  

Assume that you have the following packages loaded:

```{r message=FALSE}
library('kableExtra')
library('tidyverse')
library('caret')

# Output function for printing to pdf
tbl_out = function(df, rows = 10){
  head(df, rows) %>%
    kable() %>%
    kable_styling()
  }
```


Given the `iris` data set (first 10 rows shown below):  
```{r}
dat = iris %>% as_tibble()
tbl_out(dat)
```

\newpage

In words, describe what you would expect this to return:
```{r echo=TRUE, message=FALSE, eval=FALSE}
dat %>% 
  sample_n(nrow(dat)) %>%
  tbl_out()
```
  -  
  -  
  -  
  -  
  -  
  -  
  -  
  -  
  -  
  -  
  

Assuming your data is "clean" and your EDA has been accomplished. What steps would you take to get your data prepared for a classification algorithm?  
  -  
  -  
  -  
  -  
  -  
  -  
  -  
  -  
  -  
  -  

\newpage 
  
Show the rough code you would use to get your data ready and then train a model using `caret` and show how you would analyze and look at the results.   -  
```{r}
# Step 1: Class variable 
set.seed(123)
dat_clean <- dat %>% rename(Class = Species) 

dat_clean <- dat_clean %>% mutate(id = row_number())

# Step 2: Train Split
dat_train <- dat_clean %>%
 sample_frac(0.75)

dat_test <- dat_clean %>%
 anti_join(dat_train, by = 'id') %>%
 select(-id)

dat_train <- dat_train %>%
 select(-id)

# Step 3: Pre Process - Standarize Training Data
mod_pp <- preProcess(dat_train, method = c('scale','center'))
dat_train_pp <- predict(mod_pp, dat_train) 

```

```{r}
# Step 4: Resample as needed
dat_train_up <- upSample(x = dat_train_pp %>% select(-Class), y = dat_train_pp$Class)
```

```{r}
# Step 5: Train a Model
train_control <- trainControl(
  method = 'cv',
  number = 5
)

model_ranger = train(
  dat_train_up %>% select(-Class),
  dat_train_up$Class,
  method = "ranger",
  importance = "impurity",
  trControl = train_control,
)

model_ranger

```

```{r}
# Step 6: Scaled Test Data
dat_test_pp <- predict(mod_pp, dat_test)
```

```{r}
# Step 7: Predict from scaled test data
predictions <- predict(model_ranger, dat_test_pp)
```

```{r}
# Step 8: Anaylize Confusion matrix (Actuals => $Class)
confusionMatrix(predictions, dat_test_pp$Class)
```

```{r}
# Step 9: Variable importance
plot(varImp(model_ranger))
```

